### 2017-11-15 README.Rmd
update (partially) to everhartlab dockerhub

 1. [sclerotinia-366-dependencies](https://hub.docker.com/r/zkamvar/sclerotinia-366-dependencies/): defines the complete software environment used, built on top of the [rocker/verse:3.4.2](https://hub.docker.com/r/rocker/verse) container. **(See the [Dockerfile](https://osf.io/mwv6d/))**
 2. [sclerotinia-366](https://hub.docker.com/r/zkamvar/sclerotinia-366/) is built on top of the above container and contains the results of the analysis. **(See the [Dockerfile](https://osf.io/tvfju/))**

@@

To Install Docker, go here: https://docs.docker.com/engine/installation/#desktop. Once you have downloaded docker, you can either pull the container or build it. Pulling is by far the quickest way to do this.
The docker container is located at https://hub.docker.com/r/zkamvar/sclerotinia-366/

@@

```bash
docker run --name ssc --rm -dp 8787:8787 -e ROOT=TRUE zkamvar/sclerotinia-366:latest
```

>>>>

 1. [sclerotinia-366-dependencies](https://hub.docker.com/r/everhartlab/sclerotinia-366-dependencies/): defines the complete software environment used, built on top of the [rocker/verse:3.4.2](https://hub.docker.com/r/rocker/verse) container. **(See the [Dockerfile](https://osf.io/mwv6d/))**
 2. [sclerotinia-366](https://hub.docker.com/r/everhartlab/sclerotinia-366/) is built on top of the above container and contains the results of the analysis. **(See the [Dockerfile](https://osf.io/tvfju/))**

@@

To Install Docker, go here: https://docs.docker.com/engine/installation/#desktop. Once you have downloaded docker, you can either pull the container or build it. Pulling is by far the quickest way to do this.
The docker container is located at https://hub.docker.com/r/everhartlab/sclerotinia-366/

@@

```bash
docker run --name ssc --rm -dp 8787:8787 -e ROOT=TRUE everhartlab/sclerotinia-366:latest
```
